Enabling high resolution hydrologic routing with machine learning assisted waterbody classification

### 2024-05-13 manuscript/manuscript.tex
cleanup for preprinting

% Uncomment to override  the `A preprint' in the header
\renewcommand{\headeright}{\href{https://doi.org/}{DOI: 10.000/XXXXX}}
\renewcommand{\undertitle}{This is a draft of a Manuscript in preparation for publication in Geophysical Research Letters \href{https://doi.org/10.1000/XXXXX}{DOI: 10.1000/XXXXX}}
\renewcommand{\shorttitle}{ML assisted waterbody classification for routing}

@@

\section{Data Availability Statement}

All data and code associated with this manuscript will be made available by the time of publication (or earlier pending the conclusion of US Department of Energy approvals) with a Zenodo DOI at: \href{https://doi.org}{https://doi.org}

>>>>

% Uncomment to override  the `A preprint' in the header
\renewcommand{\headeright}{\href{https://doi.org/}{DOI: 10.000/XXXXX}}
\renewcommand{\undertitle}{This is a draft of a Manuscript in preparation for publication}
% \renewcommand{\undertitle}{This is a draft of a Manuscript in preparation for \href{https://doi.org/10.1000/XXXXX}{DOI: 10.1000/XXXXX}}
\renewcommand{\shorttitle}{ML assisted waterbody classification for routing}

@@

% \section{Data Availability Statement}

% All data and code associated with this manuscript will be made available by the time of publication (or earlier pending the conclusion of US Department of Energy approvals) with a Zenodo DOI at: \href{https://doi.org}{https://doi.org}
